Project Contract\\Local Adaptive Optimization of Timestep

### 2013-09-05 report/report.tex
Project contract done

\subsection{Problem Statement}

@@

\subsection{Success criteria}
Avoid curl ups/explosions of the grid while maintaining the original
stepsize by using local subsimulations (with smaller stepsizes)

\subsection{Risk assessment}
Low. The technique has been performed before in various shapes and it
should therefore be do-able.

>>>>

\subsection{Problem Statement}
Study the application of locally adaptive timestepping in simulation of hyperelastic materials.

@@

\subsection{Success criteria}
To gain insight into the application of LAOT.

\subsection{Risk assessment}
Low to none. The technique has been performed before in various shapes and it
should therefore be do-able.
